Outline

### 2020-10-05 text/main.Rmd
text edits

**The high diversity and productivity of coral reefs, despite their location in nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013]. Protecting reef function (cycling of elements) under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation. Here, we quantify five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans. We demonstrate that critical trade-offs exist among functions (e.g. biomass production and phosphorous cycling), and that no reef fish community worldwide can sustain high values for all five functions simultaneously. Further, functions tend to be dominated by few species, where on average ~12% of species in a community provide more than 50% of a function. However, despite such local dominance of functions by few species, most species were important somewhere; ~70% of all species contribute disproportionally to functioning in at least one local community. Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystems. Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions, so we stress the need for quantitative monitoring of multiple functions to make informed management decisions.**

The flow of elements through biological communities fuel all life on Earth [@Welti2017]. There is now strong consensus on the importance of preserving these fluxes, often termed ecosystem functions [@Welti2017]. 
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
Sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
However, in agro-ecological settings efforts to maximize one function have been shown to negatively impact another (e.g. timber vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010]. 
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging. 
Therefore, trade-offs between functions, their drivers, and vulnerability are poorly understood for many ecosystems [@Brandl2019front].

Coral reefs are among the most diverse and productive ecosystems on earth, and they provide indispensable ecosystem services to humans [@Teh2013]. 
As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic productivity [@Brandl2019science]. 
Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
Over the past decades, severe declines in coral reef habitat quality and fish biomass, and community structure shifts have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g. @Mora2011plos; @Cinner2020; @Mouillot2014]. 
Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently limits effective management [@Brandl2019front].

@@

Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers the functional variation that exists beyond biomass, the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front].
Even though we observed a strong relationship between fish standing biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig. 1), and for fish communities with similar biomass, functions tend to vary by over two orders of magnitude (Extended Data Fig. 1a). 
Thus, considering biomass alone can obscure differences in community-level functioning. 
Further, there are strong trade-offs among the different functions when taking out the effect of biomass (Fig.1, Extended Data Fig. 1b). 
For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
Strikingly, not a single community reached high biomass-corrected rates (upper 10% across all communities) for all functions. 
As a consequence, for a fixed amount of standing biomass, no reef appears to sustain high values for all of the five functions analyzed here. While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig. 1).

Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences. 
First, we explored the relationship of each function on the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e. body size, trophic level, species richness, biomass, temperature, and age structure; Fig. 2). 
We found that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig. 1b) (See also ref. @Allgeier2014). 
In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
On the other hand, fishes in early life stages that are highly dependent on phosphorus to grow, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to phosphorus excretion. 
These results emphasize the importance of fish community structure for ecosystem-wide functioning [@Schramski2015; @Allgeier2016].

Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning.   
Due to species-specific characteristics, certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass (Fig. 3a).
For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019]. 
Therefore, we assessed the role of species by quantifying the degree to which they disproportionally induce (i.e. dominate) different functions for each community. 
We demonstrate that for most communities, functions are consistently dominated by a few species (Fig. 3b). This means for example that on average ~12% of the species in a local community contribute to more than 50% of a function.
However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
Thus, while there are almost no globally important species for a given function, most species are locally important somewhere.
Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].

The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in the Anthropocene. 
Exploitation and anthropogenic climate change have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs. 
For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017]. 
These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
Yet, herbivores have a minor contribution to phosphorus excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs. 
Higher N:P ratios may in fact favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
This is particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect coral reef ecosystems.

Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion, while loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig. 4). Fishing and loss of live corals both appear to impact species important for P excretion.
Surprisingly, although fishing pressure can heavily affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
This may be due to the high variability in unique ecosystem roles within the large pool of herbivorous fish species. 
While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to become functionally extinct in regions with high human density [@Bellwood2012]. 
While herbivores of all body sizes and functional groups are united in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
Thus, our results reflect the overall vulnerability of functions, yet does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g. @Bellwood2011).

Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020]. 
Even though increased fish biomass enhances function, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another. 
For example, marine reserves, which are the main conservation approach for coral reefs [@Graham2020], may provide benefits for herbivory, but they often offer little insurance for diversity in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020]. 
Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may leed to informed decisions to prioritize certain functions based on local needs and stressors.  
Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species identity at the local scale.
While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales. Rather, it may be beta-diversity and local differences in community structure that are most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].

Overall, our results demonstrate that managing coral reefs for ecosystem functioning is, in its simplest form, unlikely to be possible. 
While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking. 
Conserving these elemental fluxes in the 21st century will require a more nuanced approach to coral reef management.

@@

![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables. Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community. The log-transformed standing biomass was also included as a covariable, but not shown in this figure. All data was standardized to be able to compare across functions and variables. Functions were log-transformed before standardisation. Dots represent the average of the effect. Filled lines indicate the 95% credible interval, with some credible intervals being too small to visualize. Effects are not shown when their 95% CI intersects with zero. Variables are ordered by the maximum absolute effect across the five models.](../output/plots/fig2_com_slopes.png)

![Figure 3: a) Median family-level contributions to each function, relative to their contribution to biomass. Positive values mean that a family contributes more relative to its contribution to total biomass. Only the 12 most important family’s are shown here, and families are ordered by their median contribution to biomass. b) Distribution of the degree of dominance of communities per function. A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function. c) Distributions of frequency of being dominant to each function of all species across all communities. A value of 1 means that a species is always important whenever present. A species is counted as being dominant in a community if the contribution of that species is higher than the scenario in which all species contribute equally (i.e. 1 divided by the species richness). Shaded areas show the distribution of the values. Dots represent the median value, while lines indicate the interquartile range.](../output/plots/fig3_contributions.png)

@@

![Extended Data Figure 2: Fitted linear regression of each function with the log-transormed gravity to fish markets, as a proxy for fishing pressure. Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

>>>>

Affiliations

A. Green: 
Red Sea Research Center, King Abdullah University of Science and Technology 
Thuwal 23955-6900, Saudi Arabia

K.S. Munsterman: 
Department of Ecology and Evolutionary Biology, University of Michigan, Ann Arbor, Michigan 48109, USA

**The high diversity and productivity of coral reefs, despite their location in generally nutrient-poor waters, provides invaluable protection, nutrition, and services to millions of people [@Teh2013]. Protecting reef function (cycling of elements) under the escalating pressures of fishing [@Graham2017; @Ceccarelli2016: @Stuart-Smith2018] and climate change [@Hughes2017] represents the cornerstone of reef conservation. Here, we quantify five key functions—nitrogen and phosphorus cycling, biomass production, herbivory, and piscivory—mediated by reef fishes across the world’s tropical oceans. We demonstrate that critical trade-offs exist among functions (e.g. biomass production and phosphorous cycling), and that no reef fish community worldwide can sustain high values for all five functions simultaneously. Further, functions tend to be dominated by few species, where on average ~12% of species in a community provide more than 50% of a function. However, despite such local dominance of functions by few species, most species were important somewhere; ~70% of all species contribute disproportionally to functioning in at least one local community. Finally, we highlight unbalanced vulnerability across functions, suggesting that certain functions are disproportionally affected by anthropogenic stressors, destabilizing the integrity of coral reef ecosystem functioning. Our findings introduce a conundrum for coral reef conservation, in that we cannot maximize all functions simultaneously, so we stress the need for quantitative assessment of multiple functions to make informed management decisions.**

The flow of elements through biological communities fuel all life on Earth [@Welti2017]. There is now strong consensus on the importance of preserving these fluxes, a set of processes often termed ecosystem functions [@Welti2017]. 
For millennia, resources have been managed with an economic mindset to maximize desirable functions such as plant or animal biomass production [@Weisser2017]. 
Sustaining multiple functions, likely requires both high species richness and a variety of species assemblages across the landscape [@Zavaleta2010].
However, in agro-ecological settings efforts to maximize one function have been shown to negatively impact another (e.g. timber vs. erosion control), shedding light on the existence of trade-offs between functions [@Tallis2008; @Zavaleta2010]. 
An understanding of such trade-offs is required to make informed management decisions [@Rodriguez2006], but simultaneously quantifying multiple ecosystem functions is challenging. 
Therefore, trade-offs between functions, their drivers, and vulnerability are poorly understood for many ecosystems [@Brandl2019front].

Coral reefs are among the most diverse and productive ecosystems on earth, and they provide essential ecosystem services to humans [@Teh2013]. 
As coral reefs thrive in nutrient-poor waters, efficient cycling of elements is key to their characteristic high productivity [@Brandl2019science]. 
Importantly, the integrity of coral reefs is threatened by a plethora of anthropogenic stressors, such as intensive exploitation and climate change [@Hughes2017]. 
Over the past decades, severe declines in coral reef habitat quality and fish biomass, and shifts in community structure have brought coral reef functioning and services to the forefront of scientific discourse [@Williams2019; @Bellwood2019; @Brandl2019front].
Yet, our capacity to quantitatively evaluate, monitor, and compare reef functioning primarily relies on static proxies of functions, such as relative live coral cover, standing biomass of reef fishes, or functional richness based on qualitative species traits [e.g. @Mora2011plos; @Cinner2020; @Mouillot2014]. 
Conversely, we know comparatively little about elemental fluxes and their drivers (but see [@Allgeier2016]), which currently limits effective management [@Brandl2019front].

@@

*statement of importance/relevance of using excretion*

Quantifying five key ecosystem functions performed by fishes across the world's reefs uncovers the functional variation that exists beyond biomass, the most commonly employed indicator of coral reef functioning [@MacNeil2015, @Mora2011plos; @Cinner2020; @Brandl2019front].
Even though we observed a strong relationship between fish standing stock biomass and all five functions, there  is remarkable variability in reef fish functions beyond biomass (Fig. 1), and for fish communities with similar biomass, functions tend to vary by over two orders of magnitude (Extended Data Fig. 1a). 
Thus, considering biomass alone can obscure differences in community-level functioning. 
Further, there are strong trade-offs among the different functions when taking out the effect of biomass (Fig.1, Extended Data Fig. 1b). 
For example, high herbivory rates or N excretion negatively correlate with rates of P excretion.
Strikingly, not a single community reached high biomass-corrected rates (upper 10% across all communities) for all functions. 
As a consequence, for a fixed amount of standing biomass, no reef appears to possess high values for all of the five functions analyzed. While many reefs may stand out as hotspots for one function, none maximize functioning as a holistic concept (Fig. 1).

Disentangling predictors of reef fish functioning revealed important effects of both community structure and species-specific influences. 
First, we explored the relationship of each function on the community level with ecological predictors known to affect elemental fluxes [@Schiettekatte2020] (i.e. body size, trophic level, species richness, biomass, temperature, and age structure; Fig. 2). 
We found that correlations between functions are mediated by contrasting aspects of community structure (Fig. 2). 
For example, P excretion is higher in communities with a high proportion of large-bodied, mature fishes that occupy high trophic levels, thus creating positive relationships between P excretion and piscivory (Extended Fig. 1b; See @Allgeier2014). 
In contrast, biomass production is highest in communities dominated by small and/or immature fishes at lower trophic levels, creating a strong trade-off between biomass production and P excretion. 
Metabolic theory predicts that small individuals have a higher mass-specific metabolic rate, and as a consequence, small individuals have elevated consumption rates and disproportionally contribute to functions that rely on rapid energetic turnover [@Barneche2018; @Morais2020glob].
On the other hand, fishes in early life stages that are highly dependent on phosphorus for growth, and fishes with a nutrient-poor diet are often limited by phosphorus [@Schiettekatte2020], resulting in low contributions to P excretion. 
These results emphasize the importance of fish community structure for ecosystem-wide functioning [@Schramski2015; @Allgeier2016].

Alongside features of community structure, specific dominant and/or high-performing species strongly affect ecosystem functioning. 
Certain species or entire families tend to contribute more or less to a particular function, relative to their contribution to standing biomass or due to specific characteristics (Fig. 3a).
For example, because Serranidae feed on P-rich preys, they contribute disproportionally to P excretion, and many Labridae have a high growth rates making them important contributors to biomass production.
Further, abundant species can profoundly affect rates of functioning at the community level [@Ruttenberg2019; @Topor2019]. 
Therefore, we assessed the role of species by quantifying the degree to which they disproportionally induce (i.e. dominate) different functions for each community. 
We demonstrate that for most communities, functions are consistently dominated by a few species (Fig. 3b). This means for example that on average ~12% of the species in a local community contribute to more than 50% of a function.
However, the identity of these species varies dramatically (Fig. 3c), despite evidence for species assuming key functional roles across widely-dispersed locations [@Bellwood2003].
Thus, while there are almost no globally important species for a given function, most species are locally important somewhere.
Indeed, ~70% of all species contributed disproportionally to a specific function in at least one reef fish community.
Despite high species richness on coral reefs, researchers often report the existence functionally-dominant “key species” [e.g. @Bellwood2006]. 
Our results imply that while functional dominance is indeed prevalent, the identity of local dominant species can be unpredictable and variable across regions, suggesting that maintaining high levels of species richness across coral reefs is essential to sustain ecosystem functioning at the global scale [@Topor2019].

The critical importance of both reef fish community structure and species-specific contributions shines new light on the vulnerability of coral reef functioning in the Anthropocene. 
Anthropogenic stressors have caused severe changes in reef fish biomass and community structure [@Mora2011plos; @Hughes2017; @Williams2019], and our findings suggest strong effects for ecosystem functioning on reefs. 
For example, intensive fishing and associated reductions in biomass of large fishes truncates the size, age, and trophic structure of fish communities [@Graham2017]. 
These effects can enhance biomass-corrected N excretion and production [e.g. @Morais2020glob], while negatively impacting P excretion, herbivory, and piscivory (Fig. 2, Extended Data Fig. 2). 
On the other hand, climate change related declines in coral cover are often associated with a shift toward herbivores, which may help avoid algal domination [@Graham2006; @Ceccarelli2016]. 
However, herbivores have a minor contribution to P excretion [@Allgeier2014; @Schiettekatte2020], so a shift to herbivore dominance in fish communities and the subsequent decline of community-level phosphorus excretion may change the balance of nutrient cycling on reefs. 
Higher N:P ratios may favor algal growth [@Burkepile2013], and promote symbiont dominance within the coral holobiont [@Allgeier2020].
Shifts in elemental ratios may be particularly problematic when considered in conjunction with climate change, since phosphorus starvation in corals reduces their temperature threshold for bleaching [@Ezzat2016]. 
Thus, considering multiple functions paints a more nuanced and holistic picture of how human-induced shifts in reef fish community structure affect overall coral reef ecosystems.

Similarly, the species-specific vulnerability of functionally-dominant species heavily affects functioning. 
By combining species-level vulnerability scores to fishing and coral loss caused by climate change [@Graham2011] with the contributions of each species to each function, we demonstrate that removal of individuals most vulnerable to fishing will have greatest impacts on piscivory, followed by P excretion. 
Conversely, loss of individuals due to coral mortality may disproportionally reduce P excretion, N excretion, and production (Fig. 4). 
Fishing and loss of live corals both appear to impact species important for P excretion.
Surprisingly, although fishing pressure can negatively affect large herbivores such as parrot fishes [@Bellwood2011], herbivory is the least vulnerable function. 
This may be due to the high variability in unique ecosystem roles within the large pool of herbivorous fish species. 
While small herbivores are often abundant and not particularly vulnerable to fishing, larger herbivorous species are often highly targeted and are prone to functional extinction in regions with high fishing pressure [@Bellwood2012]. 
While herbivores of all body sizes and functional groups are combined in our assessment, their realized contributions to herbivory are known to be strongly complementary. 
Thus, our results reflect the overall vulnerability of functions, yet this does not consider unique roles played by a small group of species, nested in a broad function such as herbivory (e.g. @Bellwood2011).

*This is a very important point that needs more elaboration.  By losing the big parrotfishes, you lose herbivores with different functional roles. First to go are the bioeroders (e.g., Bolbo, Chlorurus microrhinus) and excavators (e.g., other big Chlorurus species).  Being left with a lot of small parrots mean you are often left with just one functional group of parrotfishes (scrapers). So I think we are missing an important point here. For example as DRB says “a reef without the bioeroding parrotfishes such as Bolbo is very different to one without them”  I see you have already cited many of DRB’s papers.  For more info on functional groups see https://www.researchgate.net/publication/237411023_Monitoring_Functional_Groups_of_Herbivorous_Reef_Fishes_as_Indicators_of_Coral_Reef_Resilience_A_practical_guide_for_coral_reef_managers_in_the_Asia_Pacifi_c_Region*

Conserving biomass, diversity, and ecosystem functioning are important objectives of contemporary conservation initiatives [@Cinner2020]. 
Even though increased fish biomass enhances functions, the strong trade-offs we reveal between key ecosystem functions introduces a conundrum for coral reef conservation, where actions to enhance one function may negatively affect another. 
For example, marine protected area's, which are one of the primary used conservation approaches for coral reefs [@Graham2020], may provide benefits for herbivory for example, but they often offer little insurance for diversity conservation in human-dominated regions [@Cinner2020] and do not protect reefs from the pervasive effects of climate change [@Graham2020]. 
Thus, measuring conservation success with biomass or solely one function (e.g. herbivory) can mask the collapse of other essential functions. 
Therefore, it is necessary to gauge the state of reef ecosystems based on multiple, complementary, process-based functions [@Brandl2019front], which may leed to informed decisions to prioritize certain functions based on local needs and stressors. 
Finally, while there is a general consensus on the role of diversity in enhancing functioning [@Zavaleta2010; @Hooper2005], we highlight the overarching importance of community structure and the identity of dominant species identity at the local scale.
While, it seems clear that maintaining diversity of fishes appears critical for functioning of reefs, our results suggest that species richness only has minor effects on individual functions at local scales. Rather, it may be beta-diversity and local differences in community structure that are most critical for maintaining function at the seascape scale, as no species appears to consistently provide high contributions for all functions simultaneously or across all sites it occurs [@Duffy2009; @Zavaleta2010].

Overall, our results demonstrate that managing coral reefs for ecosystem functioning is unlikely to be possible. 
While enhancing fish biomass is important, the variability of reef fish communities in the rates of functions representing cycling of critical elements is striking. 
Conserving these elemental fluxes in the 21st century will require a more nuanced approach to coral reef management.

@@

![Figure 2: Fixed effect values of the Bayesian linear regression for each function with community variables. Trophic level, size, and immaturity of the community are represented by the median, and lower and upper 95% quantiles of all individuals inside a community. The log-transformed standing stock biomass was also included as a covariable, but not shown in this figure. All data was standardized to compare across functions and variables. Functions were log-transformed before standardisation. Dots represent the average of the effect. Horizontal lines indicate the 95% credible interval, with some credible intervals being too small to visualize. Effects are not shown when their 95% CI intersects with zero. Variables are ordered by the maximum absolute effect across the five models.](../output/plots/fig2_com_slopes.png)

![Figure 3: a) Median family-level contributions to each function, relative to their contribution to biomass. Positive values mean that a family contributes more relative to its contribution to total biomass. Only the 12 most important families are shown here, and families are ordered by their median contribution to biomass. b) Distribution of the degree of dominance of communities per function. A degree of dominance of 0 means each species contributes equally to a function, 1 means a single species performs a function. c) Distributions of frequency of being dominant to each function of all species across all communities. A value of 1 means that a species is always important whenever present. A species is counted as being dominant in a community if the contribution of that species is higher than the scenario in which all species contribute equally (i.e. 1 divided by the species richness). Shaded areas show the distribution of the values. Dots represent the median value, while lines indicate the interquartile range.](../output/plots/fig3_contributions.png)

@@

![Extended Data Figure 2: Fitted linear regression of each function with the log-transformed gravity to fish markets, as a proxy for fishing pressure. Functions are represented by their residuals, coming from the regression with biomass and sea surface temperature, and are standardized for comparison across functions.](../output/plots/annex_fig3_gravity_markets.png)

### 2020-10-05 text/suppl_methods.Rmd
text edits

### 1.1 Data compilation
We first compiled maximum lengths for all species with Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$ . For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to  equal to its maximum length [i.e. $k_{max}$, @Morais2018]. $t0$ was kept constant at 0 for all species.

@@

For each species, otoliths were cut transversely, using a diamond disc saw (Presi Mecatome T210) to obtain a section of 500 μm. Sections were then fixed on a glass side with thermoplastic glue (Crystalbond TM). Small otoliths were directly embedded in the thermoplastic glue and polished until obtained of a transversal section. Otoliths were sanded with abrasive discs of decreasing grain size (2,400 and 1,200 grains cm- 130 2) and polished with a 0.25 μm diamond suspension in order to be closest to the nucleus. All sections were photographed under a Leica DM750 light microscope with a Leica ICC50 HD microscope camera and LAS software (Leica Microsystems).

@@

We then used the Modified Fry back-calculation model (MF) [@Vigliola2000]. to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).

@@

\noindent We extrapolated $kmax$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.  
There is currently no streamlined method to make predictions to new species from a phylogenetic regression model. We circumvent the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model. We subsequently predicted these phylogenetic effects for missing species with the help of the function phyEstimate in the picante package for R [@Kembel2010]. This function uses phylogenetic ancestral state estimation to infer trait values for new species on a phylogenetic tree by rerooting the tree to the parent edge for the node to be predicted [@Kembel2012]. We repeated this for all 100 trees and 1000 draws. Per draw, we averaged the extrapolated values per species for the hundred trees. Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa$ for each species. We only use one chain in order to keep computational time reasonable. Finally, we summarised all $\kappa$ predictions per sst per species by taking the mean and standard deviation across the 1000 draws.

>>>>

### 1.1 Data compilation
We first compiled maximum lengths for all species with Fishbase [@Froese2018] and used these lengths for the $l_{\infty}$ . For $\kappa$, we used a standardized coefficient that describes the potential growth trajectory of an individual if $l_{\infty}$ were to be equal to its maximum length [i.e. $k_{max}$, @Morais2018]. $t0$ was kept constant at 0 for all species.

@@

For each species, otoliths were cut transversely, using a diamond disc saw (Presi Mecatome T210) to obtain a section of 500 μm. Sections were then fixed on a glass side with thermoplastic glue (Crystalbond TM). Small otoliths were directly embedded in the thermoplastic glue and polished until obtaining a transversal section. Otoliths were sanded with abrasive discs of decreasing grain size (2,400 and 1,200 grains cm- 130 2) and polished with a 0.25 μm diamond suspension in order to be closest to the nucleus. All sections were photographed under a Leica DM750 light microscope with a Leica ICC50 HD microscope camera and LAS software (Leica Microsystems).

@@

We then used the Modified Fry back-calculation model (MF) [@Vigliola2000] to estimate fish length at previous ages, modified to also investigate the uncertainty around the obtained length estimates using a Bayesian approach (fishgrowbot, ref).

@@

\noindent We extrapolated $kmax$ for all species across the full temperature range in which those species occur in the database, with temperature rounded to the °C, which results in 4712 unique temperature and species combinations.  
There is currently no streamlined method to make predictions for new species from a phylogenetic regression model. We circumvented the issue by extracting draws of the phylogenetic effect, $\gamma_\textrm{0phy}$ for each species included in the model. We subsequently predicted these phylogenetic effects for missing species with the help of the function phyEstimate in the picante package for R [@Kembel2010]. This function uses phylogenetic ancestral state estimation to infer trait values for new species on a phylogenetic tree by rerooting the tree to the parent edge for the node to be predicted [@Kembel2012]. We repeated this for all 100 trees and 1000 draws. Per draw, we averaged the extrapolated values per species for the hundred trees. Then, by combining the predicted phylogenetic effects with the global intercept and slopes for body size and temperatures for each draw, we predicted $\kappa$ for each species. We only use one chain in order to keep computational time reasonable. Finally, we summarised all $\kappa$ predictions per sst per species by taking the mean and standard deviation across the 1000 draws.
